Article Draft

### 2023-06-08 manuscript/draft.qmd
Adds new directory for reproducible manuscript

---
title: "Modeling Article Draft"
format: 
  html:
    self-contained: true
editor: source
execute: 
  echo: false
  warning: false
  error: false
number-sections: true
bibliography: WAIS-trends.bib
---

@@

![The region of interest in central West Antarctica and the data sets used for this study. Background image denotes 1-km resolution surface topography as a hillshade, derived from the DEM in \citet{slater_new_2018}. Colored lines show elevation contours (150 m intervals). NASA OIB Snow radar results from PAIPR are shown in red and firn/ice core locations are denoted with blue triangles. The figure also denotes the location of WAIS Divide Camp.](Figures/data_panel.png){#fig-datamap}

>>>>

---
title: "Article Draft"
format: 
  html:
    self-contained: true
editor: source
execute: 
  echo: false
  warning: false
  error: false
number-sections: true
bibliography: WAIS-trends.bib
---

@@

![The region of interest in central West Antarctica and the data sets used for this study. Background image denotes 1-km resolution surface topography as a hillshade, derived from the DEM in @slater_new_2018. Colored lines show elevation contours (150 m intervals). NASA OIB Snow radar results from PAIPR are shown in red and firn/ice core locations are denoted with blue triangles. The figure also denotes the location of WAIS Divide Camp.](figures/data_panel.png){#fig-datamap}
